Making a package from base R files

### 2022-01-27 PkgFromRbase/PkgFromRbaseBlog.Rmd
blog version

---
title: "Making a package from base R files"
author: 
   - John C. Nash \thanks{ retired professor, Telfer School of Management, University of Ottawa}
   - Arkajyoti Bhattacharjee \thanks{Department of Mathematics and Statistics, Indian Institute of Technology, Kanpur}
   - based on communications from Duncan Murdoch
date: "11/06/2021, revised 19/01/2022"
bibliography: ../BibSupport/ImproveNLS.bib
output:
  pdf_document: default
---

@@

It is worth mentioning that the NAMESPACE file provided by Duncan is an
important part of the packaging. It could be worthwhile to document each
elements in that file needed for a package such as `nlspkg`, but at the
time of writing, this is yet to be carried out. However, we must note 
that in renaming the package from `nlspkg` to something
else, the change of name must be mirrored in the line

>>>>

---
title: "Making a package from base R files"
author: 
   - John C. Nash, retired professor, Telfer School of Management, University of Ottawa
   - Arkajyoti Bhattacharjee, Department of Mathematics and Statistics, Indian Institute of Technology, Kanpur
   - based on communications from Duncan Murdoch
date: "11/06/2021, revised 19/01/2022"
bibliography: ../BibSupport/ImproveNLS.bib
output:
  html_document: default
---

@@

It is worth mentioning that the NAMESPACE file provided by Duncan is an
important part of the packaging. It could be worthwhile to document each
element in that file needed for a package such as `nlspkg`, but at the
time of writing, this is yet to be carried out. However, we must note 
that in renaming the package from `nlspkg` to something
else, the change of name must be mirrored in the line
